---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE,
  warning = FALSE
)
```

# nisracolours

<!-- badges: start -->
<!-- badges: end -->

nisracolours provides accessible colour palettes for use in charts. These palettes can be used to style charts created using ggplot2. This is also a basic example package with functions, documentation and a pkgdown website. 

## Installation

You can install the development version of nisracolours like so:

``` r
# install.packages("pak")
pak::pak("nistatisticsresearchagency/nisracolours")
```

## Usage

The easiest way to use nisracolours is to use the `scale_fill/colour_discrete_nisra()` functions:

```{r plot-1}
#| fig.alt: >
#|   Line chart of GDP per capita for France and Germany, 1952 to 2007, coloured
#|   taken from the Gapminder dataset. Both increase over time, but Germany
#|   has slightly higher GDP per capita throughout. The lines are coloured using
#|   the NISRA colour palette.     
library(nisracolours)
library(ggplot2)
library(gapminder)

subset(gapminder, country %in% c("Germany", "France")) |> 
  ggplot(aes(year, gdpPercap, colour = country)) +
  geom_line() +
  scale_colour_discrete_nisra() +
  theme_bw()
```
